---
title: "Business Intelligence Project"
author: "<Ayan Ahmed>"
date: "<17th November>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        |127039 ... |
| **Student Name**                             |Ayan Ahmed ... |
| **BBIT 4.2 Group**                           | .C.. |

#load dataset
```{r}
library(readr)
loan_dataset <- read_csv("Data/loan_dataset.csv")
View(loan_dataset)

```


#install packages 
```{r}
if (require("pROC")) {
  require("pROC")
} else {
  install.packages("pROC", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## dplyr ----
if (require("dplyr")) {
  require("dplyr")
} else {
  install.packages("dplyr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

#check data frequency
```{r}

loan_dataset_freq <- loan_dataset$loan_status
cbind(frequency =
        table(loan_dataset_freq),
      percentage = prop.table(table(loan_dataset_freq)) * 100)
```


#split the data
```{r}
if (!is.element("caret", installed.packages()[, 1])) {
  install.packages("caret", dependencies = TRUE)
}
require("caret")
train_index <- createDataPartition(loan_dataset$loan_status,
                                   p = 0.75,
                                   list = FALSE)
loan_dataset_train <- loan_dataset[train_index, ]
loan_dataset_test <- loan_dataset[-train_index, ]

```

#train the model
```{r}
train_control <- trainControl(method = "cv", number = 13)

```


#accuracy and kappa
```{r}
set.seed(7)
loan_dataset_model_glm <-
  train(loan_status ~ ., data = loan_dataset_train, method = "glm",
        metric = "Accuracy", trControl = train_control)
```

#print model performance
```{r}
print(loan_dataset_model_glm)
```


#applying 5-fold cross validation resampling method
```{r}
train_control <- trainControl(method = "cv", number = 13)
loan_dataset_caret_model_rpart <- train(loan_status ~ ., data = loan_dataset,
                                    method = "rpart", metric = "Accuracy",
                                    trControl = train_control)

```

#print the model 
```{r}
print(loan_dataset_caret_model_rpart)
```

#predictions 
```{r}
predictions <- predict(loan_dataset_caret_model_rpart,
                       loan_dataset_test[, 1:13],
                       type = "raw")

```

#model performance 
```{r}
table(predictions, loan_dataset_test$loan_status)
```

#comparing model performance - LDA,CART ,KNN
```{r}
train_control <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
```

#LDA
```{r}
set.seed(7)
loan_dataset_model_lda <- train(loan_status ~ ., data = loan_dataset,
                            method = "lda", trControl = train_control)
```

#CART
```{r}
set.seed(7)
loan_dataset_model_cart <- train(loan_status ~ ., data = loan_dataset,
                             method = "rpart", trControl = train_control)
```

#KNN
```{r}
set.seed(7)
loan_dataset_model_knn <- train(loan_status ~ ., data = loan_dataset,
                            method = "knn", trControl = train_control)
```

#call resamples functions 
```{r}
results <- resamples(list(LDA = loan_dataset_model_lda, CART = loan_dataset_model_cart,
                          KNN = loan_dataset_model_knn))
                         
```

#results of the resample functions 
```{r}
summary(results)
```

#box plot of the results
```{r}
scales <- list(x = list(relation = "free"), y = list(relation = "free"))
bwplot(results, scales = scales)
```

