---
title: "Business Intelligence Project"
author: "<Ayan Ahmed>"
date: "<17th November>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        |127039 ... |
| **Student Name**                             |Ayan Ahmed ... |
| **BBIT 4.2 Group**                           | .C.. |


#load the dataset 
```{r}
library(readr)
loan_dataset <- read_csv("Data/loan_dataset.csv")
View(loan_dataset)

```

#install packages
```{r}
.libPaths()
lapply(.libPaths(), list.files)

if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## plumber ----
if (require("plumber")) {
  require("plumber")
} else {
  install.packages("plumber", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

#split the model
```{r}
set.seed(9)
train_index <- createDataPartition(loan_dataset$loan_status,
                                   p = 0.80, list = FALSE)
loan_dataset_training <- loan_dataset[train_index, ]
loan_dataset_testing <- loan_dataset[-train_index, ]

set.seed(9)
train_control <- trainControl(method = "cv", number = 10)
loan_dataset_model_lda <- train(loan_status ~ ., data = loan_dataset,
                            method = "lda", metric = "Accuracy",
                            trControl = train_control)
```

#summary of the data
```{r}
print(loan_dataset_model_lda)
```

#details of the model
```{r}
print(loan_dataset_model_lda$finalModel)
```

#test model
```{r}
set.seed(9)
predictions <- predict(loan_dataset_model_lda, newdata = loan_dataset_testing)

```

#save and load model
```{r}
saveRDS(loan_dataset_model_lda, "./models/saved_loan_dataset_model_lda.rds")
# The saved model can then be loaded later as follows:
loaded_loan_dataset_model_lda <- readRDS("./models/saved_loan_dataset_model_lda.rds")
print(loaded_loan_dataset_model_lda)

predictions_with_loaded_model <-
  predict(loaded_loan_dataset_model_lda, newdata = loan_dataset_testing)

```

#create function in R
```{r}
name_of_function <- function(arg) {
  
}

```

#make predictions using the following variables
```{r}
to_be_predicted <-
  data.frame(loan_id = 1, no_of_dependents = 2, education = "Graduate", self_employed = "No" ,
             income_annum = 9600000, loan_amount = 29900000, loan_term = 12, cibil_score = 778,
             residential_assets_value = 2400000, commercial_assets_value =17600000, luxury_assets_value = 22700000, bank_asset_value = 8000000)


```

#make prediction
```{r}
predict(loaded_loan_dataset_model_lda, newdata = to_be_predicted)
```

#make prediction using fubction
```{r}
predict_loan_status <-
  function(arg_loan_id, arg_no_of_dependents, arg_education, arg_self_employed, arg_income_annum,
           arg_loan_amount, arg_loan_term, arg_cibil_score,arg_residential_assets_value,arg_commercial_assets_value,arg_luxury_assets_value,arg_bank_asset_value) {
    # Create a data frame using the arguments
    to_be_predicted <-
      data.frame(loan_id = arg_loan_id, no_of_dependents = arg_no_of_dependents,
                 education = arg_education, self_employed = arg_self_employed,
                 income_annum = arg_income_annum, loan_amount = arg_loan_amount,
                 loan_term = arg_loan_term, cibil_score = arg_cibil_score , residential_assets_value = arg_residential_assets_value, commercial_assets_value = arg_commercial_assets_value, luxury_assets_value = arg_luxury_assets_value ,
                 bank_asset_value= arg_bank_asset_value)
    
    # Make a prediction based on the data frame
    predict(loaded_loan_dataset_model_lda, to_be_predicted)
  }  
```


#exmaple of predictions
```{r}
predict_loan_status(1, 2, 'Graduate', 'No', 25489000, 345890, 12, 124, 685578, 4500000,9875000,3400000)

predict_loan_status(2, 3, 'Not Graduate', 'Yes', 2548900, 345900, 14, 124, 685878, 4657900,678000654,4590000)

```

#plumber API

```{r}
if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## plumber ----
if (require("plumber")) {
  require("plumber")
} else {
  install.packages("plumber", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

#model location
```{r}
loaded_loan_dataset_model_lda <- readRDS("./models/saved_loan_dataset_model_lda.rds")

```

#model description
```{r}
#* @apiTitle loan Prediction Model API

#* @apiDescription Used to predict whether a loan request  is approved or rejected.
#* 

#* @param arg_loan_id loan unique identifier
#* @param arg_no_of_dependents dependents on the loan
#* @param arg_education level of education
#* @param arg_self_employed employement status
#* @param arg_income_annum annual income
#* @param arg_loan_amount amount of loan needed
#* @param arg_loan_term loan term
#* @param arg_cibil_score cibil score
#* @param arg_residential_assets_value residence value
#* @param arg_commercial_assets_value commercial value
#* @param arg_luxury_assets_value luxury value
#* @param arg_bank_asset_value bank value


#* @get /loan_status
```

#prediction using data framework
```{r}
predict_loan_status <- function(arg_loan_id, arg_no_of_dependents, arg_education, arg_self_employed, arg_income_annum,
                                arg_loan_amount, arg_loan_term, arg_cibil_score, arg_residential_assets_value,
                                arg_commercial_assets_value, arg_luxury_assets_value, arg_bank_asset_value) {
  # Create a data frame using the arguments
  to_be_predicted <- data.frame(loan_id = as.numeric(arg_loan_id),
                                no_of_dependents = as.numeric(arg_no_of_dependents),
                                education = as.factor(arg_education),
                                self_employed = as.factor(arg_self_employed),
                                income_annum = as.numeric(arg_income_annum),
                                loan_amount = as.numeric(arg_loan_amount),
                                loan_term = as.numeric(arg_loan_term),
                                cibil_score = as.numeric(arg_cibil_score),
                                residential_assets_value = as.numeric(arg_residential_assets_value),
                                commercial_assets_value = as.numeric(arg_commercial_assets_value),
                                luxury_assets_value = as.numeric(arg_luxury_assets_value),
                                bank_asset_value = as.numeric(arg_bank_asset_value))
  # Make a prediction based on the data frame
  predict(loaded_loan_dataset_model_lda, to_be_predicted)
}
```


#Run Plumber API
```{r}
if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

# STEP 1. Install and load the required packages ----
## plumber ----
if (require("plumber")) {
  require("plumber")
} else {
  install.packages("plumber", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```


```{r}
#process plumber API
#api <- plumber::plumb("project Plumber API.R")
#run API on specific port
#api$run(host = "127.0.0.1", port = 5022)
```


